Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-10 doc/icml-presentation/presentation.tex
Fixed regression figure, and slight reordering of presentation

\usepackage{tikz}
\usetikzlibrary{positioning,shapes,shadows,arrows}

@@

    \node<2->[style=box,below=0.1cm of gen] {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Gaussian Mixture Models
        \item Hidden Markov Models
        \item Latent Dirichlet Allocation
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    \node<3->[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
    \node<4->[style=box,below=0.1cm of disc] (disc-models) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Logistic Regression
        \item Latent CRFs
        \item Discriminative LDA
        %\item Semi-Latent Topic Models (Wang and Mori, 2009)
        %\item Discriminative Parsers (Liang et.\ al, 2006)
        \item \dots
      \end{itemize}
      }};
    \node<5->[style=box,below=0.1cm of disc-models] {\obj{%
      {\bf Easy to include features and tend to be more accurate.}
    }};

@@

  % Really do known Gen (HMMs, ) vs Disc (CRFs) models

    \note[item]{Would like to start by talking about the bigger picture of parameter estimation.}
    \note[item]{Discriminative Latent Variable Models are useful, but hard to learn.}
    \note[item]{Split models into generative and discriminative models.}
    \note[item]{Discriminative LVMs combine the predictive accuracy with compact expressiveness.}
    \note[item]{They have been used in several applications, e.g.\ object recognition, syntactic parsing, machine translation, etc.}
    \note[item]{Learning parameters for these models is hard because they have non-convex likelihood functions.}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}

@@

  \begin{itemize}
    \item<1-> Log-likelihood function is non-convex.
    \item<2-> MLE is consistent but intractable.
    \item<3-> EM is efficient but inconsistent.
    \item<4-> Can we build {\bf efficient yet consistent estimators} that get better with more data?
  \end{itemize}

  \note[item]{We would like to develop efficient consistent estimators for discriminative LVMS.}
  \note[item]{Past approaches rely on local optimization, which are susceptible to local optima.}
  \note[item]{And they don't just go away with more data.}
  \note[item]{Recently, there has been work on consistent parameter
      estimation for generative LVMS\@. We'd like to extend their work to
      the discriminative case.}
\end{frame}

\begin{frame}
  \frametitle{Method of Moments a.k.a.\ Spectral Methods}
  \begin{itemize}
    \item<+-> Method of Moments [Pearson, 1894]
    \item<+-> Observable operator models
    \begin{itemize}
      \item Subspace identification [Ljung, 1987]
      \item Observable operator models [Jaeger, 2000]
        \note[item]{Entry point into machine learning}
      \item {\bf Hidden Markov models [Hsu et al, 2009]}
        \note[item]{Entry point into machine learning}
      \item Low-treewidth graphs [Parikh et al., 2012]
      \item Weighted finite state automata [Balle \& Mohri, 2012]
    \end{itemize}
     \item<+-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item {\bf Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{itemize} 
      \item Generative process:
      \begin{align*}
        h \in [k] &\sim \Mult(\pi) \\
        x &\sim \normal{\beta_h}{\sigma^2}.
      \end{align*}
    \end{itemize}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<2->[style=box,below=0.1cm of defn] {\objw{6cm}{%
    \begin{itemize} 
      \item Moments:
    \begin{align*}
        \action<2->{%
        \E[x|h] &= \beta_h \\
        }
        \action<3->{%
        \E[x] &= \sum_h \pi_h \beta_h \\
        }
        \action<4->{%
        \E[x\tp{2}] &= \sum_h \pi_h \beta_h{\hlmath{\tp{2}}} \\
                    &= \sum_h \pi_h (\beta_h \beta_h^T) \\
                    }
        \action<5->{%
        \E[x\tp{3}] &= \sum_h \pi_h \beta_h\tp{3}.
        }
      \end{align*}
    \end{itemize}
    }};
    %\tikzrect{1}{1};
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{1}{1};
    \node at (7,-2.5) {$\E[x\tp{2}]$};
    \node at (4.5,-2.5) {$d$};
    }
    \uncover<5->{%
    \tikzcube{black,fill=white}{(6,-4,0)}{1}{1}{1};
    \node at (7,-4.5,0) {$\E[x\tp{3}]$};
    \node at (4.5,-4.5) {$d$};
    \node at (4.5,-4.5) {$d$};
    }
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{align*}
        \action<1->{%
        x\tp{3}_{ijk} &= x_i x_j x_k \comment{indexing}\\
        }
        \action<2->{%
        A \cdot B &= \sum_{ijk} A_{ijk} B_{ijk} \comment{inner product}\\
        }
        \action<3->{%
        A(u)_{ij} &= \sum_{k} A_{ijk} u_k \comment{projection}\\
        }
        \action<4->{%
        A(u,v)_{i} &= \sum_{jk} A_{ijk} u_j v_k \comment{projection} \\
        }
      \end{align*}
    }};
    \tikzcube{black,fill=white}{(6,2,0)}{1}{1}{1};
    \node (pt) at (5.75,1.75,0) {$\hlmath{\times}$};
    \uncover<3->{%
    \tikzrect{black,fill=white}{(6,0)}{1}{1};
    }
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{0.1}{1};
    }
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (moments) at (0,0) {\objw{6cm}{%
      Assume $\beta_h$ to be orthogonal;
      \begin{align*}
        \E[x\tp{3}] &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<1-> at (0,-3) {\objw{6cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2->[style=box] at (6,-3) {\objw{6cm}{%
      $\beta_h$ are eigenvectors!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}

        \hfill{\em Anandkumar, Hsu, et.\ al (2012)}
      }};
%
%    \node<2>[style=box,below=0.1cm of tensorf] {\objw{12cm}{%
%    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor-decomp.png}
%      \hfill {Tensor Power Method}
%      }};
  \end{tikzpicture}

    \note[item]{\bf We can recover the means of a generative LVM by exploiting their symmetric structure.}
    \note[item]{\begin{align*} M_2 &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & M_3 &= \sum_{h=1}^k \pi_h \beta_h\tp{3}.  \end{align*}}
      \note[item]{In general, $M_2$ is insufficient to identify the model, because it is invariant to rotations of $B$. }
      \note[item]{If the $\beta_h$ were orthogonal, then the eigenvectors and eigenvalues of $M_3$ would give us the answer. }
      \note[item]{In general, we need both $M_2$ and $M_3$. We can use the whitening transformation for $M_2$ to whiten $M_3$ such that it has a orthogonal decomposition.}
      \note[item]{The robust tensor power method by \cite{AnandkumarHsuGe2012} find stable eigenvectors.}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{4cm}{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc.png}
      \begin{itemize}
        \item<2-> $h \in [k] \sim \Mult(\pi)$.
        \item<4-> $y = \beta_h^T x + \epsilon$.
      \end{itemize}
      }};

@@

% \begin{frame}
%   \frametitle{Method of Moments for Generative LVMs.}
% 
%   \begin{tikzpicture}
%     % x, y
%     \node<1->[style=box]  (moments) at (0,0) {\objw{12cm}{%
%       \begin{align*}
%         \underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
%         \underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
%         \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
%       \end{align*}
%     }};
%     \node<1>[style=box,below=0.1cm of moments] {\objw{12cm}{%
%     \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/moments.png}
%       }};
%     \node<2->[style=box,below=0.1cm of moments] {\objw{12cm}{%
%       \begin{itemize}
%         \item<2-> {\bf Tensor Power Method} for orthonormal $\beta_h$,
%           \begin{align*}
%             M_3(\beta_h,\beta_h) 
%               &= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
%               &= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
%               &= \pi_{h'} \beta_{h}.
%           \end{align*}
%         \item<3-> Use $M_2$ to whiten $M_3$.
%       \end{itemize}
%       }};
%   \end{tikzpicture}
% 
%     \note[item]{\bf We can recover the means of a generative LVM by exploiting their symmetric structure.}
%     \note[item]{\begin{align*} M_2 &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & M_3 &= \sum_{h=1}^k \pi_h \beta_h\tp{3}.  \end{align*}}
%       \note[item]{In general, $M_2$ is insufficient to identify the model, because it is invariant to rotations of $B$. }
%       \note[item]{If the $\beta_h$ were orthogonal, then the eigenvectors and eigenvalues of $M_3$ would give us the answer. }
%       \note[item]{In general, we need both $M_2$ and $M_3$. We can use the whitening transformation for $M_2$ to whiten $M_3$ such that it has a orthogonal decomposition.}
%       \note[item]{The robust tensor power method by \cite{AnandkumarHsuGe2012} find stable eigenvectors.}
% \end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{
          y &= \underbrace{\beta_h^T}_{\textrm{random}} x + \epsilon \\
          }
          \action<+->{
            &= \underbrace{\E[\beta_h]^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - \E[\beta_h])^T x + \epsilon}_{\textrm{noise}} \\
          }
        \end{align*}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}

    \note[item]{The powers of the response variables $y^p$ are linear measurements of the moments of the parameters $M_p$!}
    \note[item]{As noted earlier, the first problem we run into is that we can't observe the moments of the parameters $B$ and $\pi$ directly!}
    \note[item]{However, observe that 
    \begin{align}
      y &= \innerp{\beta_h}{x} + \epsilon \\
        &= \innerp{\E[\beta_h]}{x} + \underbrace{{\beta_h - \E[\beta_h]}{x} + \epsilon }_{\textrm{noise}},
    \end{align}
    where $M_1 = \sum_{h=1}^k \pi_h \beta_h$, the mean regression coefficient.}
    \note[item]{We note that while the noise term is dependent on $x$, it has a zero-mean. Thus, we could potentially recover $M_1$ through regression.}
    \note[item]{Similarly, we can cast the remaining two terms as regression problems.}
    \note[item]{An additional fact that we can exploit is that both $M_2$ and $M_3$ are low rank, so we can use low-rank regression to recover estimates $\hat M_2$ and $\hat M_3$ efficiently from data.}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{%
            y &= \underbrace{\E[\beta_h]^T \odot x}_{\textrm{linear measurement}} &\quad & + \underbrace{(\beta_h - \E[\beta_h])^T x + \epsilon}_{\textrm{noise}} \\
          }
          \action<+->{%
            y^2 
              &= \E[\beta_h\tp{2}] \odot x\tp{2} &+ \textrm{bias} &+ \textrm{noise} \\
          }
          \action<+->{%
          y^3 &= \E[\beta_h\tp{2}] \odot x\tp{3} &+ \textrm{bias} &+ \textrm{noise} \\
          }
        \end{align*}

        \uncover<4->{%
          We can use regression to recover $M_p$ from linear measurements.\\
          }
      }};
  \end{tikzpicture}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
      \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2->[style=box,below=0.1cm of measurements] {\objw{12cm}{%
      We can use low-rank regression techniques [Negabhan \& Wainwright 2009; Tomioka 2011].
      \begin{align*}
        \hat\E[\beta_h\tp{2}] &= \arg\min_{M} \left(y^2 - M] \odot x\tp{2}\right)^2_{(x,y)\in\mathcal{D}} + \|M\|_{*} \\
        \|M\|_{*} &= \sum_i \sigma_i(M).
      \end{align*}
      }};
  \end{tikzpicture}
\end{frame}

% \begin{frame}
%   \frametitle{Method of Moments for the Mixture of Linear Regressions.}
% 
%   \begin{tikzpicture}
%     % x, y
%     \node[style=box] (note) at (0,0) {\objw{12cm}{%
%       {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
%       }};
%     \node[style=box,below=0.1cm of note] {\objw{12cm}{%
%       \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-1.png}
%       \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-2.png}
%       \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-3.png}
%       }};
%   \end{tikzpicture}
% \end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      }};
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Perturbation Analysis}

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      %\includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-2.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-3.png}
      %\includegraphics<4>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-4.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-5.png}
      }};
  \end{tikzpicture}

>>>>

\usepackage{tikz}
\usetikzlibrary{calc,positioning,shapes,shadows,arrows}

@@

    \node<2->[style=box,below=0.1cm of gen] {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Gaussian Mixture Models
        \item Hidden Markov Models
        \item Latent Dirichlet Allocation
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    \node<3->[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
    \node<4->[style=box,below=0.1cm of disc] (disc-models) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Latent CRFs
        \item Discriminative LDA
        \item Mixture of Experts
        %\item Semi-Latent Topic Models (Wang and Mori, 2009)
        %\item Discriminative Parsers (Liang et.\ al, 2006)
        \item \dots
      \end{itemize}
      }};
    \node<5->[style=box,below=0.1cm of disc-models] {\obj{%
      {\bf Easy to include features and tend to be more accurate.}
    }};

@@

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \hfill{\em expected negative log-likelihood}
      }};
  \end{tikzpicture}

@@

  \begin{itemize}
    \item<1-> Log-likelihood function is non-convex.
    \item<2-> MLE is consistent but intractable.
    \item<3-> Local methods (EM, gradient descent, etc.) are tractable but inconsistent.
    \item<4-> Can we build {\bf efficient yet consistent estimators} that get better with more data?
  \end{itemize}

@@

\begin{frame}
  \frametitle{Related Work}
  \begin{itemize}
    \item<+-> Method of Moments [Pearson, 1894]
    \item<+-> Observable operator models
    \begin{itemize}
      \item Subspace identification [Ljung, 1987]
      \item Observable operator models [Jaeger, 2000]
      \item {\em Hidden Markov models [Hsu et al, 2009]}
      \item Low-treewidth graphs [Parikh et al., 2012]
      \item Weighted finite state automata [Balle \& Mohri, 2012]
    \end{itemize}
     \item<+-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item {\bf Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{align*}
        \action<1->{%
        x\tp{3}_{ijk} &= x_i x_j x_k \comment{tensoring}\\
        }
        \action<2->{%
        \innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk} \comment{inner product}\\
        }
        \action<3->{%
        A(u)_{ij} &= \sum_{k} A_{ijk} u_k \comment{projection}\\
        }
        \action<4->{%
        A(u,v)_{i} &= \sum_{jk} A_{ijk} u_j v_k \comment{projection} \\
        }
      \end{align*}
    }};
    \tikzcube{black,fill=white}{(6,2,0)}{1}{1}{1};
    %\node (pt) at (5.75,1.75,0) {$\hlmath{\times}$};
    \uncover<3->{%
    \tikzrect{black,fill=white}{(6,0)}{1}{1};
    }
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{0.1}{1};
    }
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{itemize} 
      \item Generative process:
      \begin{align*}
        h &\sim \Mult(\pi) \\
        x &\sim \normal{\beta_h}{\sigma^2}.
      \end{align*}
    \end{itemize}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<2->[style=box,below=0.1cm of defn] {\objw{6cm}{%
    \begin{itemize} 
      \item Moments:
    \begin{align*}
        \action<2->{%
        \E[x|h] &= \beta_h \\
        }
        \action<3->{%
        \E[x] &= \sum_h \pi_h \beta_h \\
        }
        \action<4->{%
        \E[x\tp{2}] &= \sum_h \pi_h (\beta_h \beta_h^T) \\
                    &= \sum_h \pi_h \beta_h{\tp{2}} \\
                    }
        \action<5->{%
        \E[x\tp{3}] &= \sum_h \pi_h \beta_h\tp{3}.
        }
      \end{align*}
    \end{itemize}
    }};
    %\tikzrect{1}{1};
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{1}{1};
    \node at (7,-2.5) {$\E[x\tp{2}]$};
    \node at (4.5,-2.5) {$d$};
    }
    \uncover<5->{%
    \tikzcube{black,fill=white}{(6,-4,0)}{1}{1}{1};
    \node at (7,-4.5,0) {$\E[x\tp{3}]$};
    \node at (4.5,-4.5) {$d$};
    \node at (4.5,-4.5) {$d$};
    }
  \end{tikzpicture}

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (moments) at (0,0) {\objw{6cm}{%
      If $\beta_h$ are orthogonal;
      \begin{align*}
        \E[x\tp{3}] &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<1-> at (6,-3) {\objw{6cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2->[style=box] at (0,-3) {\objw{6cm}{%
      $\beta_h$ are eigenvectors!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}

        \hfill{\em Anandkumar, Hsu, et.\ al (2012)}
      }};
%
%    \node<2>[style=box,below=0.1cm of tensorf] {\objw{12cm}{%
%    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor-decomp.png}
%      \hfill {Tensor Power Method}
%      }};
  \end{tikzpicture}
\end{frame}

    \node[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
  \end{tikzpicture}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{4cm}{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc.png}
      \begin{itemize}
        \item<2-> $h \sim \Mult(\pi)$.
        \item<4-> $y = \beta_h^T x + \epsilon$.
      \end{itemize}
      }};

@@

% \begin{frame}
%   \frametitle{Method of Moments for Generative LVMs.}
% 
%   \begin{tikzpicture}
%     % x, y
%     \node<1->[style=box]  (moments) at (0,0) {\objw{12cm}{%
%       \begin{align*}
%         \underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
%         \underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
%         \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
%       \end{align*}
%     }};
%     \node<1>[style=box,below=0.1cm of moments] {\objw{12cm}{%
%     \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/moments.png}
%       }};
%     \node<2->[style=box,below=0.1cm of moments] {\objw{12cm}{%
%       \begin{itemize}
%         \item<2-> {\bf Tensor Power Method} for orthonormal $\beta_h$,
%           \begin{align*}
%             M_3(\beta_h,\beta_h) 
%               &= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
%               &= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
%               &= \pi_{h'} \beta_{h}.
%           \end{align*}
%         \item<3-> Use $M_2$ to whiten $M_3$.
%       \end{itemize}
%       }};
%   \end{tikzpicture}
% 
% \end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{
          y &= \underbrace{\beta_h^T}_{\textrm{random}} x + \epsilon \\
          }
          \action<+->{
            &= \underbrace{\E[\beta_h]^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - \E[\beta_h])^T x + \epsilon}_{\textrm{noise}} \\
          }
        \end{align*}
      }};
  \end{tikzpicture}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{%
          y &= \underbrace{\innerp{\E[\beta_h]^T}{x}}_{\textrm{linear measurement}} &\quad & + \underbrace{(\beta_h - \E[\beta_h])^T x + \epsilon}_{\textrm{noise}} \\
          }
          \action<+->{%
            y^2 
            &= \innerp{\E[\beta_h\tp{2}]}{x\tp{2}} &+ \textrm{bias} &+ \textrm{noise} \\
          }
          \action<+->{%
          y^3 &= \innerp{\E[\beta_h\tp{3}]}{x\tp{3}} &+ \textrm{bias} &+ \textrm{noise} \\
          }
        \end{align*}

        \uncover<4->{%
        We can use regression to recover $\E[\beta_h\tp{p}]$ from linear measurements.\\
          }
      }};

    \node<5->[style=box,below=0.1cm of measurements.south] (tensor) {\objw{12cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/tensor.png}
      }};

  \begin{tikzpicture}
    % x, y
    % Nodes
    \node[style=txt] (data1) at (0,0) {$\left\{ x, y \right\}_{(x,y) \in \sD}$};
    \node[style=txt,below=1cm of data1.center] (data2) {$\left\{ x\tp{2}, y^2 \right\}_{(x,y) \in \sD}$};
    \node[style=txt,below=1cm of data2.center] (data3) {$\left\{ x\tp{3}, y^3 \right\}_{(x,y) \in \sD}$};

    \node[style=txt] (m1) at (4,0) {$\E_h\left[\beta_h\right]$};
    \node[style=txt,below=1cm of m1.center] (m2) {$\E_h\left[\beta_h\tp{2}\right]$};
    \node[style=txt,below=1cm of m2.center] (m3) {$\E_h\left[\beta_h\tp{3}\right]$};

    \node[below=0.5cm of m2.center] (params-pos) {};
    \node[style=txt,right=3.0cm of params-pos] (params) {$\pi, B$};

    % Arrows
    \draw[-latex] (data1) -- (m1);
    \draw[-latex] (data2) -- (m2);
    \draw[-latex] (data3) -- (m3);

    % Bias influence
    \draw[-latex,dashed,gray] (m1.east) -- ++(0.1cm,0) -- ++(0,-0.50cm) -- ++(-3.00cm,0) node (bias-1) {} -- ( bias-1 |- m3) -- (m3.west);

    % Mean
    \draw[-latex] (m2.east) -- ++(0.1cm,0) node (tf-1) {} -- (tf-1 |- params-pos) -- node[above,scale=0.5] {tensor factorization} (params);
    \draw[-latex] (m3.east) -- ++(0.1cm,0) node (tf-2) {} -- (tf-2 |- params-pos) -- (params);

    % Box for regression
    \begin{pgfonlayer}{bg}
    \draw[fill=blue,opacity=0.1,dashed] ($(data1.north east) + (-0.1cm,0.1cm)$) rectangle ($(m3.south west) + (0.1cm,-0.1cm)$);
    \end{pgfonlayer}
    \node[style=txt] (reg-label) at ($(data3) !.5! (m3) + (0, -1.0cm)$) {regression};

    % tensor factorization
    \begin{pgfonlayer}{bg}
    \draw[fill=green,opacity=0.1,dashed] ($(m2.north east) + (-0.1cm,0.1cm)$) rectangle ($(params.south west) + (0.1cm,-1.0cm)$);
    \end{pgfonlayer}
    \node (params-mid) at ($(params-pos) !.5! (params)$) {};
    \node[style=txt] at (params-mid |- reg-label) {tensor factorization};
  \end{tikzpicture}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] (reg) at (0,0) {\objw{12cm}{%
      \begin{align*}
        \hat\E[\beta_h\tp{2}] &= \arg\min_{M} \left(y^2 - \innerp{M}{x\tp{2}}\right)^2_{(x,y)\in\mathcal{D}} \action<3->{+ \hlmath{\|M\|_{*}}} \\
        \action<3->{%
        \|M\|_{*} &= \sum_i \sigma_i(M).
        }
      \end{align*}
      }};
    \node<2->[style=box,below=0.1 of reg] (measurements) {\objw{12cm}{%
      \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
  \end{tikzpicture}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    % Nodes
    \node[style=txt] (data1) at (0,0) {$\left\{ x, y \right\}_{(x,y) \in \sD}$};
    \node[style=txt,below=1cm of data1.center] (data2) {$\left\{ x\tp{2}, y^2 \right\}_{(x,y) \in \sD}$};
    \node[style=txt,below=1cm of data2.center] (data3) {$\left\{ x\tp{3}, y^3 \right\}_{(x,y) \in \sD}$};

    \node[style=txt] (m1) at (4,0) {$\E_h\left[\beta_h\right]$};
    \node[style=txt,below=1cm of m1.center] (m2) {$\E_h\left[\beta_h\tp{2}\right]$};
    \node[style=txt,below=1cm of m2.center] (m3) {$\E_h\left[\beta_h\tp{3}\right]$};

    \node[below=0.5cm of m2.center] (params-pos) {};
    \node[style=txt,right=3.0cm of params-pos] (params) {$\pi, B$};

    % Arrows
    \draw[-latex] (data1) -- (m1);
    \draw[-latex] (data2) -- node[above,scale=0.5] {low rank} (m2);
    \draw[-latex] (data3) -- node[above,scale=0.5] {low rank} (m3);

    % Bias influence
    \draw[-latex,dashed,gray] (m1.east) -- ++(0.1cm,0) -- ++(0,-0.50cm) -- ++(-3.00cm,0) node (bias-1) {} -- ( bias-1 |- m3) -- (m3.west);

    % Mean
    \draw[-latex] (m2.east) -- ++(0.1cm,0) node (tf-1) {} -- (tf-1 |- params-pos) -- node[above,scale=0.5] {tensor factorization} (params);
    \draw[-latex] (m3.east) -- ++(0.1cm,0) node (tf-2) {} -- (tf-2 |- params-pos) -- (params);

    % Box for regression
    \begin{pgfonlayer}{bg}
    \draw[fill=blue,opacity=0.1,dashed] ($(data1.north east) + (-0.1cm,0.1cm)$) rectangle ($(m3.south west) + (0.1cm,-0.1cm)$);
    \end{pgfonlayer}
    \node[style=txt] (reg-label) at ($(data3) !.5! (m3) + (0, -1.0cm)$) {regression};
